Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex
typo

\noindent\textbf{Contributions}\quad In this work, we propose a
framework to perform interactive visualization of complex 3D digital
structures combined with a dynamic curvature tensor estimation. More
precisely, we define a fully data parallel process on GPU hardware \todo{Definir GPU au cas ou ?} to
both efficiently extract adaptive isosurface and compute per vertex
curvature tensor using Integral Invariants estimators. Hence, this
system allows us to visualize curvature tensor in realtime on large
dynamic objects. Our approach combines a GPU implementation of
pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of
integral invariant curvature estimations.

@@

Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
$\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigvenvector
corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
results can be found in \cite{ChapterIICurvature}.\todo[inline]{Changer
ChapterIICurvature dans le bibtex...}

@@

As a consequence, for all these integral invariant based approaches,
we need to consider different ball radius which could be time
consuming when implemented on CPU. We propose here a fully parallel
implementation on GPU allowing us to change the radius and thus update
the estimated quantities in realtime.

@@

\subsection{Per Vertex Realtime Computation on GPU}

>>>>

\noindent\textbf{Contributions}\quad In this work, we propose a
framework to perform interactive visualization of complex 3D digital
structures combined with a dynamic curvature tensor estimation. More
precisely, we define a fully data parallel process on GPU hardware \todo{Definir GPU au cas ou ?} to
both efficiently extract adaptive isosurface and compute per vertex
curvature tensor using Integral Invariants estimators. Hence, this
system allows us to visualize curvature tensor in real-time on large
dynamic objects. Our approach combines a GPU implementation of
pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of
integral invariant curvature estimations.

@@

Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
$\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigenvector
corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
results can be found in \cite{ChapterIICurvature}.\todo[inline]{Changer
ChapterIICurvature dans le bibtex...}

@@

As a consequence, for all these integral invariant based approaches,
we need to consider different ball radius which could be time
consuming when implemented on CPU. We propose here a fully parallel
implementation on GPU allowing us to change the radius and thus update
the estimated quantities in real-time.

@@

\subsection{Per Vertex Real-time Computation on GPU}
